Vesicle-vesicle adhesion in linear flows: dynamics and rheology

### 2019-01-09 vesicle_code/docs/adhesion/adhesion.tex
put in extensional doublet work

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow}

@@

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially placed symmetrically on the $x$ axis in a quiescent flow
($\chi = 0$).  Once they reach steady-state doublet, the extensional
background flow is started.  We use this example to characterize the
required extensional rate to overcome the adhesive forces of the
doublet.  In particular, we investigate the effect of the reduced area.
For all the simulations, the length of the vesicles are fixed, while the
area is changed to achieve the desired reduced area.

@@

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.03$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.05$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.
  After time $t=400$, the vesicles extensional rate has overcome the
  adhesive force, and the vesicles continue to separate.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image01.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image02.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image03.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image04.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image05.png}
  \includegraphics[width = 0.16\textwidth]{figs/extensional_adR4em1adS7em1Chi1p1em1_ra080_image06.png}
  \caption{Two vesicles in an extensional flow.  The reduced area is
  $0.8$, the adhesion strength is $0.7$, and the adhesion length scale
is $0.4$, extensional rate is $\chi = 0.11$.}
\end{figure}

%We consider two vesicles suspended in the extensional flow $\uu =
%\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
%initially place symmetrically on the $y$ axis so that the background
%velocity drives the vesicles towards one another.  We vary the reduced
%area and the two vdW parameters and characterize the possible steady
%state configurations.  For all the simulations, the length of the
%vesicles are fixed, while the area is changed to achieve the desired
%reduced area.
%
%\begin{figure}[htp]
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep1.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep2.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep3.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep4.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra040_timestep5.pdf}
%  \caption{Two vesicles in an extensional flow.  The reduced area is
%  $0.40$, the adhesion strength is $1.0$, and the adhesion length scale
%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
%\end{figure}
%
%\begin{figure}[htp]
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep1.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep2.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep3.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep4.pdf}
%  \includegraphics[width = 0.19\textwidth]{figs/extensional_adR8em1adS1e0_ra090_timestep5.pdf}
%  \caption{Two vesicles in an extensional flow.  The reduced area is
%  $0.90$, the adhesion strength is $1.0$, and the adhesion length scale
%is $0.8$, background flow strength is $\chi = 10^{-2}$.}
%\end{figure}

\newpage % so that the figures are more organized writing the paper
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
so that the background velocity drives the vesicles towards one another.
In the absence of adhesion, once the vesicles are sufficiently close,
they are deflected to opposite sides of the $y$ axis, and the result is
that the distance between the vesicles goes to infinity.  However, in
the presence of adhesion, is it possible that the adhesive force keeps
the vesicles from separating, resulting in the formation of a {\em
doublet}~\cite{}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a quiescent flow} 
\label{sec:qflow}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in an extensional flow} 
\label{sec:eflow} 
We consider two vesicles suspended in the extensional flow $\uu =
\chi(-x,y)$, where $\chi$ is the extensional rate.  The vesicles are
initially placed symmetrically on the $x$ axis in a quiescent flow
($\chi = 0$).  Once they reach steady-state doublet, the extensional
background flow is started.  We use this example to characterize the
required extensional rate to overcome the adhesive forces of the
doublet.  In particular, we investigate the effect of the reduced area.
For all the simulations, the length of the vesicles are fixed, while the
area is changed to achieve the desired reduced area.

@@

\begin{figure}[htp]
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image01.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image02.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image03.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image04.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image05.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi3em2_ra080_image06.png}
  \caption{\label{fig:extensional1} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.03$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image01.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image02.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image03.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image04.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image05.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi5em2_ra080_image06.png}
  \caption{\label{fig:extensional2} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.05$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image01.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image02.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image03.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image04.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image05.png}
  \includegraphics[width = 0.15\textwidth]{figs/extensional_adR4em1adS7em1Chi1em1_ra080_image06.png}
  \caption{\label{fig:extensional3} Two vesicles in an extensional flow.
  The reduced area is $0.8$, the adhesion strength is $0.7$, and the
  adhesion length scale is $0.4$, extensional rate is $\chi = 0.1$.
  After time $t=400$, the vesicles extensional rate has overcome the
  adhesive force, and the vesicles continue to separate.}
\end{figure}

Whether the doublet is broken or not and the inclination angle of the
doublet depends on the extensional rate and the vesicles' reduced area.
A phase diagram of the steady-state configuration is in
Figure~\ref{fig:extensionalPhaseDiagram}.  Final configurations that
remain symmetric to the flow (Figure~\ref{fig:extensional1} are
indicated by red dots, tilt to some inclination angle
(Figure~\ref{fig:extensional2} are indicated by blue dots, and that
separate (Figure~\ref{fig:extensional3}) are indicated by green dots.

\begin{figure}[htp]
  \includegraphics[width=0.5\textwidth]{figs/extensional_adR4em1adS7em1_phaseDiagram.pdf}
  \caption{\label{fig:extensionalPhaseDiagram} Phase diagram of vesicle
  hydrodynamics in an extensional flow.  At a fixed Hamaker constant
  $\sigma=0.7$ and adhesion length scale $\delta=0.4$, doublets may
  either remain symmetric to the flow (red marks), or tilt to some
  inclination angle (blue dots), or the extensional rate, $\chi$, may
  overcome the adhesive force (green dots).}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Adhesion of two vesicles in a shear flow}
\label{sec:sflow} 
We consider two vesicles suspended in the shear flow $\uu = \chi(y,0)$,
where $\chi$ is the shear rate.  The vesicles are placed on the $y$ axis
so that the background velocity drives the vesicles towards one another.
In the absence of adhesion, once the vesicles are sufficiently close,
they are deflected to opposite sides of the $y$ axis, and the result is
that the distance between the vesicles goes to infinity.  However, in
the presence of adhesion, is it possible that the adhesive force keeps
the vesicles from separating, resulting in the formation of a {\em
doublet}~\cite{}.
